#General Journal Analytics for R
Below are the results for your data. Additional detail is available in the /output directory.  

The following tests were performed...     

1. Reconciliation
	 a. Journal lines and trial balance net to 0
	 b. Journal lines and trial balance activity reconcile
2. Summary Statistics
	 a. System/manual journal lines
	 b. Summary statistics by user
3. Data Quality Indicators
	 a. Journal lines with blank user
	 b. Journal lines with blank account
	 c. Journals that do not net to 0 
	 d. Journal lines with an invalid effective date
	 e. Journal lines with an effective date outside test period
	 f. Journal lines with a negative debit or credit amount
	 g. Journal lines with a blank posted date
	 h. Journal lines with blank entry description
	 i. Percent of COA without activity
4. Journal Analytics
	 a. Journal lines posted on weekends or holidays
	 b. Duplicate lines to the same account
	 c. Journal lines with same preparer and approver
	 d. Journal lines to unrelated accounts
	 e. Journal lines with blank or little description
	 f. Journal lines with key words in description
	 g. Journal lines with round dollar amount
	 h. Journal lines with recurring ending digits
	 i. Large credits to revenue at cutoff
	 j. Relationship between reserve and corresponding accounts
	 k. Effective date earlier than posted date (% of lines, >15, >30, >60, >90, >120)
	 l. Benford curve compared leading two digits  

## Import and process data  
```{r}
source("import.r")
source("gla.r")
```
 
Amounts rounded to nearest...
```{r}
div
```
  
## Results  

###1a: Journal lines and trial balance net to 0
```{r echo=FALSE}
txt1a_gl
txt1a_tb
```

###1b: Journal lines and trial balance activity reconcile
The follow accounts do *not* reconcile between the ledger and trial balance.
```{r echo=FALSE}
recon
```

###2a: System/manual journal lines
```{r echo=FALSE}
plot2a
```

###2b: Summary statistics by non-system user
```{r echo=FALSE}
print("Top 10 Users by Mean Debit")
head(gl_debits[order(-rank(mean))],10)
print("Top 10 Users by Max Debit")
head(gl_debits[order(-rank(max))],10)
plot2b_dr

print("Top 10 Users by Mean Credit")
head(gl_credits[order(rank(mean))],10)
print("Top 10 Users by Min Credit")
head(gl_credits[order(rank(min))],10)
plot2b_cr
```
Note: See output folder for top 10 debit and credit line detail.


###3a: Journal lines with blank user
```{r echo=FALSE}
txt3a_man
txt3a_sys
```


###3b: Journal lines with blank account
```{r echo=FALSE}
txt3b_man
txt3b_sys
```


### 3c: Journals that do not net to 0 
```{r echo=FALSE}
txt3c
```
Note: See output folder for unbalanced journal detail.


###4c: Journal lines with same preparer and approver
```{r echo=FALSE}
plot4c
```

